Modeling Time-Variable Elemental Abundances in Coronal Loop Simulations

### 2024-07-05 src/tex/ms.tex
[showyourwork] overleaf sync

\section*{Acknowledgments}
\textbf{All of the tools used to produce this paper are open-source.}  At the time of writing, the implementation into \texttt{ebtel++} is publicly available as an unmerged pull request on GitHub: \url{https://github.com/rice-solar-physics/ebtelPlusPlus/pull/87}.

@@

\software{
\texttt{ebtel++} (\url{https://github.com/rice-solar-physics/ebtelPlusPlus/pull/87}),
\texttt{matplotlib} \citep{hunter_matplotlib:_2007}, \texttt{showyourwork!} \citep{luger2021}
}

>>>>

\section*{Acknowledgments}
\textbf{All of the tools used to produce this paper are open-source.}  The implementation into \texttt{ebtel++} is publicly available on GitHub: \url{https://github.com/rice-solar-physics/ebtelPlusPlus}.

@@

\software{
\texttt{ebtel++} (\url{https://github.com/rice-solar-physics/ebtelPlusPlus}),
\texttt{matplotlib} \citep{hunter_matplotlib:_2007}, \texttt{showyourwork!} \citep{luger2021}
}
